---
title: "Capstone Project - Tennis Analysis"
author: "Sandra Barbuti"
date: "March 3, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introduction
This code imports all files associated with 2013 Grand Slam Tennis Tournaments. There are 8 files imported - 4 men and 4 women for each of the 4 grand slam tournaments. The 8 files are merged into 1 dataset called 'tennisdata'.


```{r message=FALSE}
setwd("C:/Users/Sandra/Documents/DataScienceCert/Data")
library(plyr)
library(dplyr)
paths <- dir(path = "C:/Users/Sandra/Documents/DataScienceCert/Data", pattern = "\\.csv")
names(paths) <- basename(paths)
tennisdata <- ldply(paths, read.csv)
tennisdata <- rename(tennisdata, tournamentname=.id)
```

##Summary
Summary of all tennisdata variables.

```{r warning=FALSE}
summary(tennisdata)
```

##Basic Statistics 
Calculates mean and standard deviation of each variable

```{r warning=FALSE}
tennisdata %>% 
  summarise_each(funs(mean,sd(., na.rm=TRUE)))
```

#Manipulate dataset
Takes tournament name field and splits it into 3 different variables.  
* I am able to strip 3 fields out of 1 field but I am having trouble with the titles. Why are they in a different format. The fields are called - ex. tournamentname.format instead of just format.  
* Also, I don't need the variable named format, how can i remove it? The methods I tried below do not work. Am thinking it has something to do with the question above.  
```{r warning=FALSE}
#substring
library(reshape2)
tennisdata2 <- transform(tennisdata, tournamentname = colsplit(tennisdata$tournamentname, "[-.]", c("Tournament", "Gender", "Year", "Format")))
#why can i not remove the format variable i created from the dataframe?
#tennisdata3 <- subset(tennisdata2, select = -c(tennisdata2$tournamentname.Format))
#varremove <- names(tennisdata2) %in% c("Format")
#tennisdata3 <- tennisdata2[!varremove]
```

#Logistic Regression
Runs logistic regression using the outcome as the independent variable.  
*This seems to work fine.
```{r warning=FALSE}
#testing logistic regression works
myvars <- c("Result","ACE.1","ACE.2")
tennisdata1 <- tennisdata[myvars]
model <- glm(Result ~.,family=binomial(link='logit'),data=tennisdata1)
summary(model)
```

Runs logistic regression with all variables.  

*Why does this not work? All p values = 1. Why? 
```{r warning=FALSE}
mylogit <- glm(Result ~ FNL.1 + FNL.2 +	FSP.1 +	FSW.1 +	SSP.1 +	SSW.1 +	ACE.1 +	DBF.1 +	WNR.1 +	UFE.1 +	BPC.1 +	BPW.1 +	NPA.1 +	NPW.1 +	TPW.1 +	ST1.1 +	ST2.1 +	ST3.1 +	ST4.1 +	ST5.1 +	FSP.2 +	FSW.2 +	SSP.2 +	SSW.2 +	ACE.2 +	DBF.2 +	WNR.2 +	UFE.2 +	BPC.2 +	BPW.2 +	NPA.2 +	NPW.2 +	TPW.2 +	ST1.2 +	ST2.2 +	ST3.2 +	ST4.2 +	ST5.2, data = tennisdata2, family = "binomial")
summary(mylogit)
```

Use train and test

```{r warning=FALSE}
library(caTools)
set.seed(1000)
split =  sample.split(tennisdata2$Result, SplitRatio = .70)
train = subset(tennisdata2, split ==TRUE)
test = subset(tennisdata2, split == FALSE)
tennislog = glm(Result ~ FNL.1 + FNL.2 +	FSP.1 +	FSW.1 +	SSP.1 +	SSW.1 +	ACE.1 +	DBF.1 +	WNR.1 +	UFE.1 +	BPC.1 +	BPW.1 +	NPA.1 +	NPW.1 +	TPW.1 +	ST1.1 +	ST2.1 +	ST3.1 +	ST4.1 +	ST5.1 +	FSP.2 +	FSW.2 +	SSP.2 +	SSW.2 +	ACE.2 +	DBF.2 +	WNR.2 +	UFE.2 +	BPC.2 +	BPW.2 +	NPA.2 +	NPW.2 +	TPW.2 +	ST1.2 +	ST2.2 +	ST3.2 +	ST4.2 +	ST5.2 , data = train, family=binomial)
summary(tennislog)
predictTest = predict(tennislog, type = "response", newdata = test)
table(test$Result, predictTest > 0.5)
library(ROCR)
ROCPred = prediction(predictTest, test$Result)
as.numeric(performance(ROCPred,"auc")@y.values)
```

#Correlations

Testing a few variables
```{r warning=FALSE}
cor(train[c("Result","FNL.1","FNL.2")])  
```
