---
title: "Capstone Project - Tennis Analysis"
author: "Sandra Barbuti"
date: "March 3, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introduction
This code imports all files associated with 2013 Grand Slam Tennis Tournaments. There are 8 files imported - 4 men and 4 women for each of the 4 grand slam tournaments. The 8 files are merged into 1 dataset called 'tennisdata'.


```{r message=FALSE}
setwd("C:/Users/Sandra/Documents/DataScienceCert/Data")
library(plyr)
library(dplyr)
paths <- dir(path = "C:/Users/Sandra/Documents/DataScienceCert/Data", pattern = "\\.csv")
names(paths) <- basename(paths)
tennisdata <- ldply(paths, read.csv)
tennisdata <- rename(tennisdata, tournamentname=.id)
```

##Summary
Summary of all tennisdata variables.

```{r warning=FALSE}
summary(tennisdata)
```

##Basic Statistics 
Calculates mean and standard deviation of each variable

```{r warning=FALSE}
tennisdata %>% 
  summarise_each(funs(mean,sd(., na.rm=TRUE)))
```

#Logistic Regression
Runs logistic regression using the outcome as the independent variable. 

```{r warning=FALSE}
myvars <- c("Result","ACE.1","ACE.2")
tennisdata1 <- tennisdata[myvars]
model <- glm(Result ~.,family=binomial(link='logit'),data=tennisdata1)
summary(model)
```
