---
title: "Tennis Analysis"
author: "Sandra Barbuti"
date: "March 3, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introduction
This code imports all files associated with 2013 Grand Slam Tennis Tournaments. There are 8 files imported - 4 men and 4 women for each of the 4 grand slam tournaments. The 8 files are merged into 1 dataset called 'tennisdata'.


```{r message=FALSE}
setwd("C:/Users/Sandra/Documents/DataScienceCert/Data")
library(plyr)
library(dplyr)
paths <- dir(path = "C:/Users/Sandra/Documents/DataScienceCert/Data", pattern = "\\.csv")
names(paths) <- basename(paths)
tennisdata <- ldply(paths, read.csv)
tennisdata <- rename(tennisdata, tournamentname=.id)
```

##Basic Statistics 
Calculates mean and standard deviation of each variable

```{r warning=FALSE}
tennisdata %>% 
  summarise_each(funs(mean,sd(., na.rm=TRUE)))
```

##Renames all observations
Labels all observations with the corresponding activity labels and names respectively.


##Dataset with Averages
Create a tidy data set that contains the average of each variable for each activity. 



